The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the last glacial maximum

### 2013-06-13 sections/model.tex
Update the mass balance parameters

\begin{table}[t]
	\caption{Positive degree-day model parameters.}
	\label{tab:pdd}
	\vskip4mm
	\centering
	\begin{tabular}{ll}
		\tophline
		Parameter& Value\\
		\middlehline
		degree-day factor for snow & 3\,\unit{mm\,K^{-1}\,day^{-1}}\\
		degree-day factor for ice & 8\,\unit{mm\,K^{-1}\,day^{-1}}\\
		standard deviation of temperatures & 5\,K\\
		refreezing faction & 0.6 \\
		\bottomhline
	\end{tabular}
\end{table}

@@

\begin{equation}
	\mathrm{PDD} = \int_{t_0}^{t_1} dt \left[
		\frac{\sigma}{\sqrt{2\pi}}
		\exp\left({-\frac{T(t)^2}{2\sigma^2}}\right)
		+\frac{T(t)}{2}
		\mathrm{erfc} \left(-\frac{T(t)}{\sqrt{2}\sigma}\right)
	\right]
\end{equation}

Where $[t_0; t_1]$ is one year and $\mathrm{erfc}$ is the complementary error function. The ablation model employs different degree-day factors for snow and ice and accounts for refreezing (table~\ref{tab:pdd}).

>>>>

@@

\begin{equation}
	\mathrm{PDD} = \int_{t_0}^{t_1} dt \left[
		\frac{\sigma}{\sqrt{2\pi}}
		\exp\left({-\frac{T(t)^2}{2\sigma^2}}\right)
		+\frac{T(t)}{2}
		\mathrm{erfc} \left(-\frac{T(t)}{\sqrt{2}\sigma}\right)
	\right],
\end{equation}

where the integration interval $[t_0; t_1]$ is one week and $\mathrm{erfc}$ is the complementary error function. The ablation model uses degree-day factors of 3.04~\unit{mm\,K^{-1}\,day^{-1}} for snow and 4.59~\unit{mm\,K^{-1}\,day^{-1}} for ice, as derived from mass-balance measurements on present glaciers from the Coast and Rocky Mountains in British Columbia \citep{shea-etal-2009}.

### 2013-06-13 sections/results.tex
Update the mass balance parameters

To compare modelled ice sheets of similar size, we selected for each climate forcing the simulation that lead to a glaciated area closest to an arbitrary target of $4\,\times10^6\,\unit{km^2}$. These qualitative ``best'' runs are presented in Figure~\ref{fig:best} along the associated temperature offset values. We observe that although similar in size, the selected ice sheets are different in shape and flow patterns. More specifically, NCEP/NCAR, CFSR and ERA-Interim ice sheets cover large territories in Yukon and Alaska that where shown to have remained ice-free for at least several glacial cycles\citep{dukrodkin-1999,kaufman-manley-2004}.

>>>>

To compare modelled ice sheets of similar size, we selected for each climate forcing the simulation that lead to a glaciated area closest to an arbitrary target of $4\,\times10^6\,\unit{km^2}$. These qualitative ``best'' runs are presented in Figure~\ref{fig:best} along the associated temperature offset values. We observe that although similar in size, the selected ice sheets are different in shape and flow patterns. More specifically, NCEP/NCAR, CFSR and ERA-Interim ice sheets cover large territories in Yukon and Alaska that where shown to have remained ice-free for at least several glacial cycles \citep{dukrodkin-1999,kaufman-manley-2004}.
